Reasoning about a Capability Machine with Local Capabilities\\ Provably Safe Stack and Return Pointer Management (without OS Support)

### 2017-02-13 csf-2017/paper.tex
Examples section

\section{Examples}
In this section, we demonstrate how our formal model of capability
safety allows us to prove local state encapsulation and control-flow
integrity properties for challenging program examples.  Since we are
dealing with assembly language, there are many details to the formal
treatment, and therefore we necessarily have to omit some details in
the lemmas we state here.  The interested reader can find all the
technical details in the techincal report~\cite{XXX}.

@@

The final example, in \figurename~\ref{fig:prog-g1}, is a faithful
translation of a trciky example known from the
litterature\cite{XXX}. It consists of two parts, \texttt{g1} and
\texttt{f4}. \texttt{g1} is a closure generator that generates a
closure with one variable $x$ set to 0 in its environment and \texttt{f4} as
the program. The program \texttt{f4} expects to arguments: a stack and
a callback. The stack is necessary to use \texttt{scall}, but because
it comes from an untrusted source, we need to make sure that it has
the correct permission and fits with our stack dicipline. The callback
must be global for the program to work, we will get back to this
point. The program now sets $x$ to 0 and calls the callback. When it
returns from the callback, it sets $x$ to 1 and calls the callback a
second time. When it returns from the callback, it asserts $x$ is 1
and returns.

To illustrate how subtle this program is, consider one way an
adversary may try to make the assertion fail. In the second callback
an adversary can get to the first callback by calling the closure one
more time. If the adversary can save the protected return pointer in
the second callback and use it in the first, then the assertion will
fail because $x$ is 0 before the first callback. The protected return
pointer cannot be transfered between the callbacks, so this does not
work.

>>>>

\section{Examples}
In this section, we demonstrate how our formal model of capability
safety allows us to prove local state encapsulation and control-flow
integrity properties for challenging program examples. The security
measures of Section~\ref{sec:stack-and-return-pointer} are deployed to
ensure these properties. Since we are dealing with assembly language,
there are many details to the formal treatment, and therefore we
necessarily have to omit some details in the lemmas we state here.
The interested reader can find all the technical details in the
techincal report~\cite{XXX}.

@@

The final example, in \figurename~\ref{fig:prog-g1}, is a faithful
translation of a trciky example known from the
litterature\cite{XXX}. It consists of two parts, \texttt{g1} and
\texttt{f4}. \texttt{g1} is a closure generator that generates
closures with one variable $x$ set to $0$ in its environment and
\texttt{f4} as the program. The program \texttt{f4} expects two
arguments: a stack and a callback. The stack is necessary to use
\texttt{scall}, but because it comes from an untrusted source, we need
to make sure that it has the correct permission and fits with our
stack dicipline. The callback must be global for the program to work,
we will get back to this point. The program now sets $x$ to $0$ and
calls the callback. When it returns from the callback, it sets $x$ to
$1$ and calls the callback a second time. When it returns from the
callback, it asserts $x$ is $1$ and returns.

To illustrate how subtle this program is, consider one way an
adversary may try to make the assertion fail. In the second callback
an adversary can get to the first callback by calling the closure one
more time. If the adversary can save the protected return pointer in
the second callback and use it in the first, then the assertion will
fail because $x$ is $0$ before the first callback. The protected return
pointer cannot be transfered between the callbacks, so this does not
work.
